Component response rate variation underlies the stability of complex systems (revision notes)

### 2020-01-13 notebook/revision_notes.Rmd
New simulations and notes to show the curvature for the leading eigenvalue with rho

```{r, echo = FALSE}
rho_its  <- 1000;
sim_rhos <- rand_rho_var(S = 25, rhos = seq(from = -0.9, to = 0.9, by = 0.1), 
                         iters = rho_its);
```

@@

The curvature of the relationship between $\rho$ and $\max(\Re(\lambda))$ is consistent across different values of $S$, as shown below.

>>>>

```{r, echo = FALSE}
rho_its  <- 1000;
# sim_rhos <- rand_rho_var(S = 25, rhos = seq(from = -0.9, to = 0.9, by = 0.1), 
#                         iters = rho_its);
sim_rhos <- read.csv(file = "sim_results/rhos/sim_rhos.csv");
```

@@

The curvature of the relationship between $\rho$ and $\max(\Re(\lambda))$ is consistent across different values of $S$, as shown below. Including $\gamma$ always results in a concave upward relationship between $\rho$ and $\max(\Re(\lambda))$.

```{r, echo = FALSE, fig.height = 8, fig.width = 6}
sim10 <- read.csv(file = "sim_results/rhos/sim10_rho.csv");
sim15 <- read.csv(file = "sim_results/rhos/sim15_rho.csv");
sim20 <- read.csv(file = "sim_results/rhos/sim20_rho.csv");
sim25 <- read.csv(file = "sim_results/rhos/sim25_rho.csv");
sim30 <- read.csv(file = "sim_results/rhos/sim30_rho.csv");
sim35 <- read.csv(file = "sim_results/rhos/sim35_rho.csv");
par(mar = c(0.25, 0.25, 0.25, 0.25), mfrow = c(3, 2), oma = c(6, 6, 1, 1));
plot(x = sim10[,1], y = sim10[,20], type = "l", pch = 20, lwd = 2, xaxt = "n",
     ylim = c(-1, 3.5), cex.axis = 1.5);
points(x = sim10[,15], y = sim10[,21], type = "l", lwd = 2, lty = "dashed");
abline(h = 0, col = "red", lty = "dotted", lwd = 0.8);
text(x = -0.6, y = 3.2, labels = "S = 10", cex = 2.5);
plot(x = sim15[,1], y = sim15[,20], type = "l", pch = 20, lwd = 2, xaxt = "n",
     ylim = c(-1, 3.5), yaxt = "n", cex.axis = 1.5);
points(x = sim15[,15], y = sim15[,21], type = "l", lwd = 2, lty = "dashed");
abline(h = 0, col = "red", lty = "dotted", lwd = 0.8);
text(x = -0.6, y = 3.2, labels = "S = 15", cex = 2.5);
plot(x = sim20[,1], y = sim20[,20], type = "l", pch = 20, lwd = 2, xaxt = "n",
     ylim = c(-1, 3.5), cex.axis = 1.5);
points(x = sim20[,15], y = sim20[,21], type = "l", lwd = 2, lty = "dashed");
abline(h = 0, col = "red", lty = "dotted", lwd = 0.8);
text(x = -0.6, y = 3.2, labels = "S = 20", cex = 2.5);
plot(x = sim25[,1], y = sim25[,20], type = "l", pch = 20, lwd = 2, xaxt = "n",
     ylim = c(-1, 3.5), yaxt = "n", cex.axis = 1.25);
points(x = sim25[,15], y = sim25[,21], type = "l", lwd = 2, lty = "dashed");
abline(h = 0, col = "red", lty = "dotted", lwd = 0.8);
text(x = -0.6, y = 3.2, labels = "S = 25", cex = 2.5);
plot(x = sim30[,1], y = sim30[,20], type = "l", pch = 20, lwd = 2, 
     ylim = c(-1, 3.5), cex.axis = 1.5);
points(x = sim30[,15], y = sim30[,21], type = "l", lwd = 2, lty = "dashed");
abline(h = 0, col = "red", lty = "dotted", lwd = 0.8);
text(x = -0.6, y = 3.2, labels = "S = 30", cex = 2.5);
plot(x = sim35[,1], y = sim35[,20], type = "l", pch = 20, lwd = 2, 
     ylim = c(-1, 3.5), yaxt = "n", cex.axis = 1.5);
points(x = sim35[,15], y = sim35[,21], type = "l", lwd = 2, lty = "dashed");
abline(h = 0, col = "red", lty = "dotted", lwd = 0.8);
text(x = -0.6, y = 3.2, labels = "S = 35", cex = 2.5);
mtext(text = "E correlation between A_ij and A_ji", side = 1,
      line = 4, outer = TRUE, cex = 1.5);
mtext(text = "E leading real part eigenvalue", side = 2,
      line = 3.5, outer = TRUE, cex = 1.5);
```
